\disstitle

### 2018-06-18 chapters/fasthorizon/paper.tex
fix corrupt references
fasthorizon

\begin{figure}
  \centering
  \includegraphics[width=.48\linewidth]{fasthorizon/cover_hybrid_sampling}
  \includegraphics[width=.48\linewidth]{fasthorizon/cover_segment_clusters}

@@

\begin{figure}
  \centering
  \includegraphics[width=0.8\linewidth]{fasthorizon/homoIntersection}
  \caption{In homogeneous coordinates, lines (red lines) are defined
    by the normal (red arrow) of the plane (red triangle) they form
    with the origin (green dot). Two lines form a great circle (blue
    circle), whose normal (blue arrow) is their common point (blue
    dot) in homogeneous coordinates.}
  % \caption{In homogeneous coordinates normals (red arrow) of
  %   concurrent lines (red line) form a great circle (blue circle),
  %   whose normal (blue arrow) is their common point (blue dot) in
  %   homogeneous coordinates.}
  \label{fig:homoIntersection}
\end{figure}

@@

\begin{figure}
 \centering
 \includegraphics[width=.48\linewidth]{fasthorizon/4horpdf}
 \includegraphics[width=.48\linewidth]{fasthorizon/68horpdf}

@@

\begin{figure}
  \centering
  \includegraphics[width=.92\linewidth]{fasthorizon/independent_subset}

@@

Since they were randomly sampled, the set of vanishing points
selected during initialization, $\{\mathbf{p}_i\}_{opt}$, may not be at the
optimal locations.  We optimize their locations to further minimize
the objective function \eqref{obj}. We perform an EM-like algorithm
to refine the vanishing point locations, subject to the constraint
that they lie on the horizon line:
\begin{compactitem}

@@

\begin{table}[h]
  \centering
  \caption{
   Algorithm parameters (given an $H\times W$ image).
  }
  \vspace{-.5em}
  \begin{tabular}{|c|l|l|}
    \hline
    Name & Usage(s) & Value\\
    \hline
    $\theta_{con}$ & \secref{problem} & $2^\circ$\\
    $\rho$ & \secref{problem} & $2/\operatorname{max}(H,W)$ \\
    $\kappa$ & \secref{deeplearning} & $ 1/5 \times H$ \\
    $\theta_{ver}$ & \secref{zenithdetection}, \secref{horizondetection} & $ \Theta_{\mathbf{l},\mathbf{l}_{\mathbf{z}}} < 10^\circ$ \\
    $\theta_{hor}$ & \secref{horizondetection} & $\Theta_{\mathbf{l},\mathbf{h}} <
    1.5^\circ$ \\
    $S$ & \secref{horizondetection} & 300 candidates \\
    $M$ & \secref{initialization} & 20 line segments \\
    $\theta_{dist}$ & \secref{horizondetection}, \secref{initialization} & $
    \Theta_{\mathbf{p}_i,\mathbf{p}_j} > 33^\circ$\\
    \hline
  \end{tabular}
  \label{tab:parameters}
\end{table}

@@

\begin{table}[t] \centering
  \caption{Component error analysis (AUC).}
    %AUC performance comparison of our algorithm when major components,
    %``global context'' $+$ ``vanishing point detection'', are
    %omitted or replaced (see \secref{analysis} for details). 
  \vspace{-.5em}
  \begin{tabular}{|l|c|c|c|}
    \hline
    Method & YUD & ECD & HLW \\
    \hline
    \hline
    Lezama et al.~\cite{alignment2014} & 94.51\% & 89.20\% & 52.59\% \\
    \hline
    NONE+FULL & 93.87\% & 87.94\% & 53.04\% \\
    \hline
    GISTRF+EMPTY & 53.36\% &  32.69\% & 31.08\% \\
    GISTRF+FULL & 94.66\% &  87.60\% & 54.95\% \\
    \hline
    CNN+EMPTY & 73.67\% &  67.64\% & 49.03\% \\
    % CNN (No refinement) & 94.61\% & 89.55\% & XX \\
    CNN+FULL (Ours) & \textbf{94.78\%} & \textbf{90.80\%} & \textbf{58.24\%} \\
    \hline
  \end{tabular}
  \label{tab:contribution}
\end{table}

@@

\begin{figure}
  \centering
  \includegraphics[width=.48\linewidth]{fasthorizon/cnn_vs_nocnn_ecd_hybrid}
  \includegraphics[width=.48\linewidth]{fasthorizon/cnn_vs_nocnn_ecd_uniform}
  %
  \includegraphics[width=.48\linewidth]{fasthorizon/cnn_vs_nocnn_yud_hybrid}
  \includegraphics[width=.48\linewidth]{fasthorizon/cnn_vs_nocnn_yud_uniform}
  \caption{Two images where horizon line estimates are much better with global context (left) than without (right).}
  \label{fig:iscontext}
\end{figure}

\begin{figure*}
  \centering
  \includegraphics[width=0.1571\linewidth]{fasthorizon/montage_ecd5}
  \includegraphics[width=0.0884\linewidth]{fasthorizon/montage_ecd1}
  \includegraphics[width=0.1572\linewidth]{fasthorizon/montage_yud2}
  \includegraphics[width=0.1571\linewidth]{fasthorizon/montage_ecd4}
  \includegraphics[width=0.1572\linewidth]{fasthorizon/montage_yud3}
  \includegraphics[width=0.0884\linewidth]{fasthorizon/montage_ecd6}
  \includegraphics[width=0.1571\linewidth]{fasthorizon/montage_ecd8}
  \includegraphics[width=0.1375\linewidth]{fasthorizon/montage_ecd5_homo}
  \includegraphics[width=0.1375\linewidth]{fasthorizon/montage_ecd1_homo}
  \includegraphics[width=0.1375\linewidth]{fasthorizon/montage_yud2_homo}
  \includegraphics[width=0.1375\linewidth]{fasthorizon/montage_ecd4_homo}
  \includegraphics[width=0.1375\linewidth]{fasthorizon/montage_yud3_homo}
  \includegraphics[width=0.1375\linewidth]{fasthorizon/montage_ecd6_homo}
  \includegraphics[width=0.1375\linewidth]{fasthorizon/montage_ecd8_homo}

  \includegraphics[width=0.1540\linewidth]{fasthorizon/montage_yud1}
  \includegraphics[width=0.0867\linewidth]{fasthorizon/montage_ecd3}
  \includegraphics[width=0.1540\linewidth]{fasthorizon/montage_yud5}
  \includegraphics[width=0.1540\linewidth]{fasthorizon/montage_yud4}
  \includegraphics[width=0.1731\linewidth]{fasthorizon/montage_ecd2}
  \includegraphics[width=0.1540\linewidth]{fasthorizon/montage_yud6}
  \includegraphics[width=0.0867\linewidth]{fasthorizon/montage_ecd7}
  \includegraphics[width=0.1375\linewidth]{fasthorizon/montage_yud1_homo}
  \includegraphics[width=0.1375\linewidth]{fasthorizon/montage_ecd3_homo}
  \includegraphics[width=0.1375\linewidth]{fasthorizon/montage_yud5_homo}
  \includegraphics[width=0.1375\linewidth]{fasthorizon/montage_yud4_homo}
  \includegraphics[width=0.1375\linewidth]{fasthorizon/montage_ecd2_homo}
  \includegraphics[width=0.1375\linewidth]{fasthorizon/montage_yud6_homo}
  \includegraphics[width=0.1375\linewidth]{fasthorizon/montage_ecd7_homo}
  \caption{Example results produced by our method.  (rows 1 and 3)
    Line segments color coded based on the most consistent VP, the
    ground-truth (green dash), and detected horizon lines (magenta).
    For clarity only the top two horizontal VPs are shown.  (rows 2
    and 4) The line segments (dots) and their VPs (rings) represented
    in homogeneous coordinates. (last column) Two failure cases of our
    method, caused by irregularly shaped objects (bottom) and short
    edges (top).}
  \label{fig:examples}
\end{figure*}

>>>>

\begin{figure}
  \centering
  \includegraphics[width=.4\linewidth]{fasthorizon/cover_hybrid_sampling}
  \hfill
  \includegraphics[width=.4\linewidth]{fasthorizon/cover_segment_clusters}

@@

\begin{figure}
  \centering
  \includegraphics[width=0.6\linewidth]{fasthorizon/homoIntersection}
  \caption{In homogeneous coordinates, lines (red lines) are defined
    by the normal (red arrow) of the plane (red triangle) they form
    with the origin (green dot). Two lines form a great circle (blue
    circle), whose normal (blue arrow) is their common point (blue
    dot) in homogeneous coordinates.}
  % \caption{In homogeneous coordinates normals (red arrow) of
  %   concurrent lines (red line) form a great circle (blue circle),
  %   whose normal (blue arrow) is their common point (blue dot) in
  %   homogeneous coordinates.}
  \label{fig:homoIntersection}
\end{figure}

@@

\begin{figure}
 \centering
 \includegraphics[width=.4\linewidth]{fasthorizon/4horpdf}
 \hfill
 \includegraphics[width=.4\linewidth]{fasthorizon/68horpdf}

@@

\begin{figure}
  \centering
  \includegraphics[width=.82\linewidth]{fasthorizon/independent_subset}

@@

Since they were randomly sampled, the set of vanishing points
selected during initialization, $\{\mathbf{p}_i\}_{opt}$, may not be at the
optimal locations.  We optimize their locations to further minimize
the objective function \eqref{eq:obj}. We perform an EM-like algorithm
to refine the vanishing point locations, subject to the constraint
that they lie on the horizon line:
\begin{compactitem}

@@

\begin{table}[h]
  \centering
  \caption{
   Algorithm parameters (given an $H\times W$ image).
  }
  \vspace{-.5em}
  \begin{tabular}{|c|l|l|}
    \hline
    Name & Usage(s) & Value\\
    \hline
    $\theta_{con}$ & \secref{problem} & $2^\circ$\\
    $\rho$ & \secref{problem} & $2/\operatorname{max}(H,W)$ \\
    $\kappa$ & \secref{deeplearning} & $ 1/5 \times H$ \\
    $\theta_{ver}$ & \secref{zenithdetection}, \secref{horizondetection} & $ \Theta_{\mathbf{l},\mathbf{l}_{\mathbf{z}}} < 10^\circ$ \\
    $\theta_{hor}$ & \secref{horizondetection} & $\Theta_{\mathbf{l},\mathbf{h}} <
    1.5^\circ$ \\
    $S$ & \secref{horizondetection} & 300 candidates \\
    $M$ & \secref{initialization} & 20 line segments \\
    $\theta_{dist}$ & \secref{horizondetection}, \secref{initialization} & $
    \Theta_{\mathbf{p}_i,\mathbf{p}_j} > 33^\circ$\\
    \hline
  \end{tabular}
  \label{tbl:parameters}
\end{table}

@@

\begin{table}[t] \centering
  \caption{Component error analysis (AUC).}
    %AUC performance comparison of our algorithm when major components,
    %``global context'' $+$ ``vanishing point detection'', are
    %omitted or replaced (see \secref{analysis} for details). 
  \vspace{-.5em}
  \begin{tabular}{|l|c|c|c|}
    \hline
    Method & YUD & ECD & HLW \\
    \hline
    \hline
    Lezama et al.~\cite{alignment2014} & 94.51\% & 89.20\% & 52.59\% \\
    \hline
    NONE+FULL & 93.87\% & 87.94\% & 53.04\% \\
    \hline
    GISTRF+EMPTY & 53.36\% &  32.69\% & 31.08\% \\
    GISTRF+FULL & 94.66\% &  87.60\% & 54.95\% \\
    \hline
    CNN+EMPTY & 73.67\% &  67.64\% & 49.03\% \\
    % CNN (No refinement) & 94.61\% & 89.55\% & XX \\
    CNN+FULL (Ours) & \textbf{94.78\%} & \textbf{90.80\%} & \textbf{58.24\%} \\
    \hline
  \end{tabular}
  \label{tbl:contribution}
\end{table}

@@

\begin{figure}
  \centering
  \includegraphics[width=.4\linewidth]{fasthorizon/cnn_vs_nocnn_ecd_hybrid}
  \includegraphics[width=.4\linewidth]{fasthorizon/cnn_vs_nocnn_ecd_uniform}
  \\
  \includegraphics[width=.4\linewidth]{fasthorizon/cnn_vs_nocnn_yud_hybrid}
  \includegraphics[width=.4\linewidth]{fasthorizon/cnn_vs_nocnn_yud_uniform}
  \caption{Two images where horizon line estimates are much better with global context (left) than without (right).}
  \label{fig:iscontext}
\end{figure}

\begin{figure*}
  \centering
  \includegraphics[width=0.1571\linewidth]{fasthorizon/montage_ecd5}
  %\includegraphics[width=0.0884\linewidth]{fasthorizon/montage_ecd1}
  \includegraphics[width=0.1572\linewidth]{fasthorizon/montage_yud2}
  \includegraphics[width=0.1571\linewidth]{fasthorizon/montage_ecd4}
  \includegraphics[width=0.1572\linewidth]{fasthorizon/montage_yud3}
  \includegraphics[width=0.0884\linewidth]{fasthorizon/montage_ecd6}
  \includegraphics[width=0.1571\linewidth]{fasthorizon/montage_ecd8}
  \\
  \includegraphics[width=0.1375\linewidth]{fasthorizon/montage_ecd5_homo}
  %\includegraphics[width=0.1375\linewidth]{fasthorizon/montage_ecd1_homo}
  \includegraphics[width=0.1375\linewidth]{fasthorizon/montage_yud2_homo}
  \includegraphics[width=0.1375\linewidth]{fasthorizon/montage_ecd4_homo}
  \includegraphics[width=0.1375\linewidth]{fasthorizon/montage_yud3_homo}
  \includegraphics[width=0.1375\linewidth]{fasthorizon/montage_ecd6_homo}
  \includegraphics[width=0.1375\linewidth]{fasthorizon/montage_ecd8_homo}

  \includegraphics[width=0.1540\linewidth]{fasthorizon/montage_yud1}
  %\includegraphics[width=0.0867\linewidth]{fasthorizon/montage_ecd3}
  \includegraphics[width=0.1540\linewidth]{fasthorizon/montage_yud5}
  \includegraphics[width=0.1540\linewidth]{fasthorizon/montage_yud4}
  \includegraphics[width=0.1731\linewidth]{fasthorizon/montage_ecd2}
  \includegraphics[width=0.1540\linewidth]{fasthorizon/montage_yud6}
  \includegraphics[width=0.0867\linewidth]{fasthorizon/montage_ecd7}
  \\
  \includegraphics[width=0.1375\linewidth]{fasthorizon/montage_yud1_homo}
  %\includegraphics[width=0.1375\linewidth]{fasthorizon/montage_ecd3_homo}
  \includegraphics[width=0.1375\linewidth]{fasthorizon/montage_yud5_homo}
  \includegraphics[width=0.1375\linewidth]{fasthorizon/montage_yud4_homo}
  \includegraphics[width=0.1375\linewidth]{fasthorizon/montage_ecd2_homo}
  \includegraphics[width=0.1375\linewidth]{fasthorizon/montage_yud6_homo}
  \includegraphics[width=0.1375\linewidth]{fasthorizon/montage_ecd7_homo}
  \caption{Example results produced by our method.  (rows 1 and 3)
    Line segments color coded based on the most consistent VP, the
    ground-truth (green dash), and detected horizon lines (magenta).
    For clarity only the top two horizontal VPs are shown.  (rows 2
    and 4) The line segments (dots) and their VPs (rings) represented
    in homogeneous coordinates. (last column) Two failure cases of our
    method, caused by irregularly shaped objects (bottom) and short
    edges (top).}
  \label{fig:examples}
\end{figure*}
